The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex
updating solar system in sample plot

\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6 with
modifications by David W. Hogg and Daniel Foreman-Mackey.
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother

@@

% TO DOS
\newcommand{\todo}[3]{{\color{#2}\emph{#1}: #3}}
\newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
\newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}

@@

@@

\acknowledgments
It is a pleasure to thank
\ldots
for helpful contributions to the ideas and code presented here.

>>>>

\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
With modifications by David W. Hogg and Daniel Foreman-Mackey\\
See the last page for endnotes
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother

@@

% TO DOS
\newcommand{\todo}[3]{{\color{#2}\emph{#1}: #3}}
\newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
\newcommand{\tdmtodo}[1]{\todo{TDM}{blue}{#1}}
\newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}

@@

\tdmtodo{Just a note that I've added your figure in at the end of this section
--- DFM}

In light of this result, we demonstrate the sensitivity of our measured
occurrence rates on contamination by computing a second constraint on
$\Gamma_V$ for each volume with one candidate removed.
In this case, \eq{rate-density} would be replaced by
\begin{eqnarray}
\tilde{\Gamma}_V &\equiv&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})
          - 1}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\quad.
\end{eqnarray}
These updated rates are listed in Table~\ref{tab:occurrence}.

\begin{figure*}[htbp]~\\
\begin{center}
\includegraphics[width=\textwidth]{../prediction/shape_kdes.pdf}
\end{center}
\caption{%
\dfmfiglabel{shape-kdes}}
\end{figure*}

@@

\acknowledgments
It is a pleasure to thank
So Hattori,
Angie Wolfgang,
and
Hans-Walter Rix
for helpful contributions to the ideas and code presented here.
